---
title: ACF report
author: Tomas Lenc
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  html_document:
    code_folding: hide
    toc: true
    toc_float:
      collapsed: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

source('config.R')
source('figures.R')
source('utils.R')

```


This report compiles all simulations and analyses for the paper "Measuring self-similarity in empirical signals to understand musical beat perception".  

```{r}
# load matlab parameters 
par_matlab <- drop(R.matlab::readMat(file.path(data_path, 'ir-square_ir.mat'), fixNames=FALSE)$par)

only_use_f0_harmonics <- ifelse('true', 'false', par_matlab$only_use_f0_harmonics)
keep_band <- ifelse('true', 'false', par_matlab$ap_band_around_harmonics[2] > 1)

```



Frequencies of interest for FFT were selected as follows:   

**Meter-related freqs**: `r round(par_matlab$freq_meter_rel, 2)` Hz. 

**Meter-unrelated freqs**: `r round(par_matlab$freq_meter_unrel, 2)` Hz. 

<br> 

Lags of interest for ACF were selected as follows:   

**Meter-related lags**: `r round(par_matlab$lags_meter_rel, 2)` s. 

**Meter-unrelated lags**: `r round(par_matlab$lags_meter_unrel, 2)` s.  

<br>  

# Simulations 

<br><br>

## Sensitivity 

The figure below show the sensitivity of the magnitude spectrum based and autocorrelation based analysis to periodic 
recurrence at the beat rate, which was manipulated by changing the magnitude of unitary responses at different positions
within a long simulated sequence.  

```{r, fig.align="center"}
fname <- file.path(data_path, 'ir-square_emph.svg')
knitr::include_graphics(fname)
```

<br>  <br>  

The figure below shows the sensitivity to decreasing periodic recurrence as a function of increasing jitter (this can be
thought of as manipulating phase stability of a periodic signal).  

```{r, fig.align="center"}
fname = list.files(path=data_path, 
           pattern='ir-square_apFitMethod-irasa_onlyHarm-.*_jitter.svg')

knitr::include_graphics(file.path(data_path, fname))
```

<br><br><br>

## Specificity

The figure below shows how magnitude spectrum and autocorrelation based methods behave when the periodic recurrence is 
fixed and the shape of the unnitary event is changing.  


```{r, fig.align="center"}
fname <- file.path(data_path, 'ir-square_ir.svg')
knitr::include_graphics(fname)
```

<br><br>

Below is the result of simulating many signals with identical arrangement of unitary events in time, and changing the 
shape of the unitary response randomly across simulated sequences.  

Only the z-scored acf is invariant.  

```{r}

fname <- 'ir-rand_ir.csv'
df_ir <- read.csv(file.path(data_path, fname))

df_ir_long <- pivot_longer(df_ir,
                           !sample, 
                           names_to='method',
                           values_to='value')

df_ir_long$method <- factor(df_ir_long$method, 
                            levels=c('zscore', 'ratio', 'contrast', 'r'))

df_ir_long$value <- round(df_ir_long$value, 9)

p <- ggplot(df_ir_long, aes(x=0, y=value, group=method)) + 
    # geom_half_violin(side='l', scale='width',
    #              fill='grey60', color=NA, alpha=1, trim=T) + 
    # geom_half_point(side='r', alpha=0.1, color='black') + 
    geom_point(position=position_jitter(height=0, width=0.1), alpha=0.1) + 
    facet_wrap(~ method, scales='free_y', nrow=1) + 
    xlim(c(-0.5, 0.5)) + 
    theme_cowplot() + 
    theme(
        axis.line.x = element_blank(), 
        axis.text.x = element_blank(), 
        axis.ticks.x = element_blank(), 
        axis.text.y = element_text(size=fontsize), 
        axis.title = element_text(size=fontsize), 
        axis.title.x = element_blank(),
        strip.background = element_blank(), 
        strip.text = element_text(size=fontsize, face='bold')
    ) 

save_fig(file.path(data_path, fname), p, width=5, height=3)
p

```

<br><br><br><br>  


## Effect of noise  

<br> 


Noise is bad because it distorts the shape of the magnitude DFT or ACF, creating a bias in the estimated zscore. 

This can be easily demonstrated by applying the estimation method to pure noise without any signal. 

When we repeat this simulation many times, we see that simply applying the magnitude spectrum-based or autocorrelation-based 
method leads to, on average, non-zero beat-related zscore. 

To address this issue, there are ways to account for the noise and minimize the bias:   

* DFT -> subtracting neighboring bins in the magnitude spectrum.  
* ACF -> estimating the 1/f noise and subtracting this estimate from the spectrum before computing the ACF.  


```{r}

fname = list.files(path=data_path, 
           pattern='ir-square_noise-eeg_apFitMethod-irasa_onlyHarm-.*_onlyNoise.csv')

df_only_noise <- read.csv(file.path(data_path, fname))

df_only_noise$sample <- seq(1, nrow(df_only_noise))
    
df_only_noise_long <- pivot_longer(df_only_noise,
                                   !sample, 
                                   names_to='method',
                                   values_to='z_meter')

get_bf <- function(df) {
       bf <- BayesFactor::ttestBF(df$z_meter, mu=0)
       data.frame(bf10 = sprintf('BF10=%.3g', as.vector(bf)),
                  z_meter=0.05 + max(df$z_meter))
}

df_bf <- df_only_noise_long %>% 
    group_by(method) %>%
    group_modify(~ get_bf(.x))

df_summary <- summarySE(data=df_only_noise_long, measurevar='z_meter', groupvars=c('method'))

p <- ggplot(df_only_noise_long, aes(x=1, y=z_meter)) + 
    geom_hline(yintercept=0, color='black', linetype='dashed') + 
    geom_half_violin(side='l', scale='width', fill='grey70', color=NA) + 
    geom_half_point(side='r', color='grey50', alpha=0.1) + 
    geom_point(data=df_summary, size=2, color='black') + 
    geom_errorbar(data=df_summary, aes(ymin=z_meter-sd, ymax=z_meter+sd),
                  color='black', linewidth=0.8, width=0) + 
    geom_text(data=df_bf, aes(label=bf10)) + 
    scale_x_continuous(breaks=c()) + 
    facet_wrap(~method, nrow=1, scales='free_y') + 
    theme_cowplot() + 
    theme(
        axis.title.x = element_blank(),
        axis.line.x = element_blank()
    )


save_fig(file.path(data_path, fname), p, width=6, height=3)
p
```




<br><br>

### Zscore: pulled to zero by noise

After making sure that noise pulls the estimated beat z-score to zero rather than some non-zero value, we still have a 
problem when applying freq-tagging in real experimental situations. 

Namely, the issue is that systematically different magnitude of noise across conditions can lead to spurious statistical 
differences in the estimated beat zscores. 

We have to minimize the effect of noise as much as possible (in reality there is no way to simply get 
rid of the influence of noise - we can only suppress it to greater/lesser degree).  

```{r}

fname = list.files(path=data_path, 
           pattern='irType-square_apFitMethod-irasa_onlyHarm-.*_noiseEffectZscore.csv')

df_noise_effect_z <- read.csv(file.path(data_path, fname))

# convert to factors
df_noise_effect_z$pat <- factor(df_noise_effect_z$pat)
df_noise_effect_z$selected_for <- factor(df_noise_effect_z$selected_for,
                                         levels=(c('fft', 'acf')))

# convert to long format so that we can use the method and/or whether noise was subtracted as an
# independent variable 
df <- pivot_longer(df_noise_effect_z,
                   !c(pat, selected_for, snr, sample, z_snr, z_meter_fft_orig, z_meter_acf_orig), 
                   names_to='var_name',
                   values_to='z_meter')

# some magic to create new variable columns about the method 
df$method <- ifelse(str_detect(df$var_name, 'fft'), 'fft', 'acf')
df$subtr <- ifelse(str_detect(df$var_name, 'subtr'), 'yes', 'no')
df$subtr <- factor(df$subtr, levels=c('no', 'yes'))

# more factors
df$snr <- factor(df$snr)
df$snr <- factor(df$snr, levels=rev(levels(df$snr)))

mask_fft <- df$selected_for == 'fft'
df$z_meter_orig <- rep(NA, 1, nrow(df))
df$z_meter_orig[mask_fft] <- df$z_meter_fft_orig[mask_fft]
df$z_meter_orig[!mask_fft] <- df$z_meter_acf_orig[!mask_fft]

p_acf_low_z <- plot_subtr_effect(df, method='acf', pats=1)
p_acf_high_z <- plot_subtr_effect(df, method='acf', pats=2)

p_fft_low_z <- plot_subtr_effect(df, method='fft', pats=3)
p_fft_high_z <- plot_subtr_effect(df, method='fft', pats=4)

# extract a legend that is laid out horizontally
legend <- get_legend(p_fft_high_z + 
                         guides(color = guide_legend(nrow = 1)) +
                         theme(legend.position="top"))
# merge plots 
p_merged <- plot_grid(
    p_fft_high_z + theme(legend.position="none"), 
    p_acf_high_z + theme(legend.position="none"), 
    p_fft_low_z + theme(legend.position="none"), 
    p_acf_low_z + theme(legend.position="none"), 
    nrow=2, ncol=2)

p <- plot_grid(legend, p_merged, ncol=1, rel_heights=c(0.1, 1))

save_fig(file.path(data_path, fname), p, width=7, height=5)
p


```


In the analysis above, we have picked a pattern that yielded a high (or low) meter zscore separately
for the DFT and for the ACF. This is because it turns out quite difficult to find a pattern that 
yields very similar zscore (**in absolute terms**) between the FFT and ACF. 

The zscores yielded by the two methods are still **higly correlated** though, but the absolute scale of 
meter zscores obtained with the two methods differs. 


<br><br>

Rather than looking at beat-related z-score, we can assess the effect of noise by looking at the individual values across 
all freqs/lags of interest (i.e. together, beat-related and unrelated).  

Using simulations, we can simply assess the how different the estimated values (i.e. magnitudes in case of DFT, or 
autocorrelation values in case of ACF) are from the known clean signal, when we add some known level of noise.  

Let's focus only on the ACF. 

We can plot the ground-truth correlation after binning the observed zSNR and estimating distribution density within each 
bin interval.   

Let's save the output directly to files. 

```{r}

# We can place the log zSNR slices such that one of them is exactly centered at the log z_snr observed 
# in the EEG dataset (either lowhigh or infant).  
# 
# This way we can get a better idea where we are in term of surface EEG data quality and what we can 
# expect in terms of reconstructing the ground truth ACF values.  
# 
# Of course, keep in mind that this simulation is done with a square impulse response kernel and resting-state
# EEG noise from a different dataset than lowhigh or infant. That means the shape of the noise, as well as the 
# unitary response will be different between the simulated data and lowhigh/infant eeg, making the z_snr values
# estimated from the first N harmonics harder to directly compare.  

fname <- 'irType-square_apFitMethod-irasa_noiseEffectDistCorrection.csv'
df <- read.csv(file.path(data_path, fname))

# plot raw ACF with average log zSNR across all subjects in the lowhigh dataset (adults)
fname_eeg = list.files(path=data_path, 
           pattern='exp-lowhigh_apFitMethod-irasa_onlyHarm-.*_roi-front_eegIndividual.csv')
df_eeg_ind <- read.csv(file.path(data_path, fname_eeg))

p <- plot_dist_to_truth_density(filter(df, method=='raw'), 
                                y_var_name='r',
                                df_eeg_z_snr=df_eeg_ind)
fname_fig <- tools::file_path_sans_ext(fname)
fname_fig_elems <- unlist(str_split(fname_fig, '_'))
fname_fig_elems[length(fname_fig_elems)] <- 'method-raw_exp-lowhigh_noiseEffectDistACF'
fname_fig <- paste(fname_fig_elems, collapse='_')
save_fig(file.path(data_path, fname_fig), p, width=5, height=3)


# plot raw ACF with average log zSNR across all subjects in the infant dataset
fname_eeg = list.files(path=data_path, 
           pattern='exp-infant_apFitMethod-irasa_onlyHarm-.*_roi-front_eegIndividual.csv')
df_eeg_ind <- read.csv(file.path(data_path, fname_eeg))

p <- plot_dist_to_truth_density(filter(df, method=='raw'), y_var_name='r',
                                df_eeg_z_snr=df_eeg_ind)
fname_fig <- tools::file_path_sans_ext(fname)
fname_fig_elems <- unlist(str_split(fname_fig, '_'))
fname_fig_elems[length(fname_fig_elems)] <- 'method-raw_exp-infant_noiseEffectDistACF'
fname_fig <- paste(fname_fig_elems, collapse='_')
save_fig(file.path(data_path, fname_fig), p, width=5, height=3)

```


<br><br>

Let's plot how it looks when we take raw ACF.  

```{r}
# let's also plot it using the exact same zSNR bin boundaries so we can assemble the figure

# plot raw ACF 
p <- plot_dist_to_truth_density(filter(df, method=='raw'), y_var_name='r')
fname_fig <- tools::file_path_sans_ext(fname)
fname_fig_elems <- unlist(str_split(fname_fig, '_'))
fname_fig_elems[length(fname_fig_elems)] <- 'method-raw'
fname_fig <- paste(fname_fig_elems, collapse='_')
save_fig(file.path(data_path, fname_fig), p, width=5, height=3)
p
```

<br><br>

Let's plot how it looks when we take 1/f-subtracted ACF.  

```{r}

# plot 1/f-subtracted ACF 
p <- plot_dist_to_truth_density(filter(df, method=='subtr'), y_var_name='r')
fname_fig <- tools::file_path_sans_ext(fname)
fname_fig_elems <- unlist(str_split(fname_fig, '_'))
fname_fig_elems[length(fname_fig_elems)] <- 'method-subtr'
fname_fig <- paste(fname_fig_elems, collapse='_')
save_fig(file.path(data_path, fname_fig), p, width=5, height=3)
p
```


<br><br>

Let's plot how it looks when we take 1/-subtracted and noise zeroed-out ACF.  

```{r}

# plot 1/f-subtracted and noise zeroed-out ACF 
p <- plot_dist_to_truth_density(filter(df, method=='subtr_only_harm'), y_var_name='r')
fname_fig <- tools::file_path_sans_ext(fname)
fname_fig_elems <- unlist(str_split(fname_fig, '_'))
fname_fig_elems[length(fname_fig_elems)] <- 'method-subtrOnlyHarm'
fname_fig <- paste(fname_fig_elems, collapse='_')
save_fig(file.path(data_path, fname_fig), p, width=5, height=3)
p
```




<br><br><br>


### Noise: band width


```{r, fig.height=15, fig.width=5}

fname <- 'irType-square_apFitMethod-irasa_noiseEffectDistBand.csv'
df <- read.csv(file.path(data_path, fname))
df$bandwidth <- factor(round(df$bandwidth, 2))

bands <- levels(df$bandwidth)

ps <- vector(mode="list", length=length(bands) + 2)

# raw 
p <- plot_dist_to_truth_density(filter(df, bandwidth == bands[1]), 
                            y_var_name='r_raw')
ps[[1]] <- p + 
    theme(axis.text.x = element_blank())

# subtr 
p <- plot_dist_to_truth_density(filter(df, bandwidth == bands[1]), 
                            y_var_name='r_subtr')
ps[[2]] <- p + 
    theme(axis.text.x = element_blank())

# subtr + band
i_offset <- length(ps) - length(bands) 
for (i_band in c(1:length(bands))){
    p <- plot_dist_to_truth_density(filter(df,  bandwidth == bands[i_band]), 
                                y_var_name='r_subtr_band')
    p <- p + 
        theme(axis.text.x = element_blank()) + 
        ggtitle(sprintf('band: %s Hz', bands[i_band]))
    ps[[i_band + i_offset]] <- p
}

p <- do.call(plot_grid, c(ps, ncol=1))

fname_fig <- tools::file_path_sans_ext(fname)
fname_fig_elems <- unlist(str_split(fname_fig, '_'))
fname_fig <- paste(fname_fig_elems, collapse='_')
save_fig(file.path(data_path, fname_fig), p, width=5, height=15)
p
```








---


<br><br><br>


# Real data 

Let's test how the method works on real data now.  


<br><br>

## EEG: LowHigh experiment


```{r}

rhythms <- c('unsyncopated', 'syncopated')
tones <- c('L', 'H')

fname_lowhigh = list.files(path=data_path, 
           pattern='exp-lowhigh_apFitMethod-irasa_onlyHarm-.*_roi-front_eegIndividual.csv')

df_eeg_ind <- read.csv(file.path(data_path, fname_lowhigh))

df_eeg_ind$rhythm <- factor(df_eeg_ind$rhythm,  levels=rhythms)
df_eeg_ind$tone <- factor(df_eeg_ind$tone,  levels=tones)

# cols <- c(L='#b52c0d', H='#1058b0')
cols <- c(L='#742b82ff', H='#a65a03ff')

cols_individual <- lighten(cols, amount=0.7)
names(cols_individual) <- names(cols)

```


### FFT

Analysis performed on a frontal cluster of channels to get better SNR.   

```{r, fig.width=2.3, fig.height=1.5}
p <- plot_feat_ind_lowhigh(df_eeg_ind, 
              col_name_eeg='z_meter_fft_subtr',
              col_name_coch='z_meter_fft_sound')

fname <- sprintf('%s_FFT', tools::file_path_sans_ext(fname_lowhigh))
save_fig(file.path(data_path, fname), p, width=2.3, height=1.4)
p

```
<br> 

Mixed model (factors: rhythm x tone)

```{r}
m <- lmer(z_meter_fft_subtr ~ rhythm * tone + (1|subject), data=df_eeg_ind)
a <- Anova(m)
knitr::kable(a)
```
<br> 

Posthoc tests low vs. high tone: 

```{r}
if (a[which(rownames(a) == 'rhythm:tone'), "Pr(>Chisq)"] < 0.05){
    
    df_posthoc <- df_eeg_ind %>% 
        group_by(rhythm) %>%
        group_modify(~posthoc_ttest_low_vs_high(.x, var_name_eeg='z_meter_fft_subtr'))
    
    df_posthoc$p <- p.adjust(df_posthoc$p, 'bonferroni')
    knitr::kable(df_posthoc)
    
} else if (a[which(rownames(a) == 'tone'), "Pr(>Chisq)"] < 0.05) {
    
    m_posthoc <- lmer(z_meter_fft_subtr ~ rhythm + tone + (1|subject), data=df_eeg_ind)
    emm <- emmeans(m_posthoc, 'tone')
    c <- contrast(emm, 'pairwise', adjust='bonferroni')
    knitr::kable(as.data.frame(c))
    
} else {
    
    print('no effect including tone signifianct...')

}
```
<br> 

T-test against 0 (fdr corrected): 
```{r}

df_posthoc <- df_eeg_ind %>% 
    group_by(rhythm, tone) %>% 
    group_modify(~ttest_0(.x, var_name='z_meter_fft_subtr'))

df_posthoc$p <- p.adjust(df_posthoc$p, method='fdr')

(df_posthoc)
```



<br><br><br> 

### ACF

Noise-subtracted acf was computed and averaged across **frontocentral** channels, separately for each participant.  

The zscore at meter-related lags was computed from the channel-averaged ACF, separately for each participant and condition.  

```{r, fig.width=2.3, fig.height=1.5}
p <- plot_feat_ind_lowhigh(df_eeg_ind, 
              col_name_eeg='z_meter_acf_subtr',
              col_name_coch='z_meter_acf_sound')

fname <- sprintf('%s_ACF', tools::file_path_sans_ext(fname_lowhigh))
save_fig(file.path(data_path, fname), p, width=2.3, height=1.4)
p
```
<br> 

Mixed model (factors: rhythm x tone)

```{r}
m <- lmer(z_meter_acf_subtr ~ rhythm * tone + (1|subject), data=df_eeg_ind)
a <- Anova(m)
knitr::kable(a)
```
<br> 

Posthoc tests low vs. high tone: 

```{r}
if (a[which(rownames(a) == 'rhythm:tone'), "Pr(>Chisq)"] < 0.05){
    
    df_posthoc <- df_eeg_ind %>% 
        group_by(rhythm) %>%
        group_modify(~posthoc_ttest_low_vs_high(.x, var_name_eeg='z_meter_acf_subtr'))
    
    df_posthoc$p <- p.adjust(df_posthoc$p, 'bonferroni')
    knitr::kable(df_posthoc)
    
} else if (a[which(rownames(a) == 'tone'), "Pr(>Chisq)"] < 0.05) {
    
    m_posthoc <- lmer(z_meter_acf_subtr ~ rhythm + tone + (1|subject), data=df_eeg_ind)
    emm <- emmeans(m_posthoc, 'tone')
    c <- contrast(emm, 'pairwise', adjust='bonferroni')
    knitr::kable(as.data.frame(c))

} else {
    
    print('no effect including tone signifianct...')
    
}

```

<br> 

T-test against 0 (fdr corrected): 
```{r}

df_posthoc <- df_eeg_ind %>% 
    group_by(rhythm, tone) %>% 
    group_modify(~ttest_0(.x, var_name='z_meter_acf_subtr'))

df_posthoc$p <- p.adjust(df_posthoc$p, method='fdr')

knitr::kable(df_posthoc)
```


### Correlation FFT~ACF

```{r}

res <- cor.test(df_eeg_ind$z_meter_fft_subtr, 
                df_eeg_ind$z_meter_acf_subtr, 
                method='pearson')

p <- plot_correlation_scatter(df_eeg_ind, 
                              'z_meter_fft_subtr',
                              'z_meter_acf_subtr',
                              corr_result=res, 
                              bins=15)


fname <- sprintf('%s_corrFftAcf', tools::file_path_sans_ext(fname_lowhigh))
save_fig(file.path(data_path, fname), p, width=4, height=4)
p

```




<br><br>

## TAPPING: LowHigh experiment


```{r}
fname_lowhigh = list.files(path=data_path, 
           pattern='exp-lowhigh_apFitMethod-irasa_onlyHarm-.*_tapIndividual.csv')

df_tap_ind <- read.csv(file.path(data_path, fname_lowhigh))

df_tap_ind$rhythm <- factor(df_tap_ind$rhythm,  levels=rhythms)
df_tap_ind$tone <- factor(df_tap_ind$tone,  levels=tones)

```


### Correlation FFT~ACF

```{r}

res <- cor.test(df_tap_ind$z_meter_fft_subtr, 
                df_tap_ind$z_meter_acf_subtr, 
                method='pearson')

p <- plot_correlation_scatter(df_tap_ind, 
                              'z_meter_fft_subtr',
                              'z_meter_acf_subtr',
                              corr_result=res, 
                              bins=15)

fname <- sprintf('%s_corrFftAcf', tools::file_path_sans_ext(fname_lowhigh))
save_fig(file.path(data_path, fname), p, width=4, height=4)
p

```

---



<br><br>

## EEG: Infant experiment

```{r}

rhythms <- c('unsync', 'sync')
tones <- c('low', 'high')

fname_lowhigh = list.files(path=data_path, 
           pattern='exp-infant_apFitMethod-irasa_onlyHarm-.*_roi-front_eegIndividual.csv')

df_eeg_ind <- read.csv(file.path(data_path, fname_lowhigh))

df_eeg_ind$rhythm <- factor(df_eeg_ind$rhythm,  levels=rhythms)
df_eeg_ind$tone <- factor(df_eeg_ind$tone,  levels=tones)

# cols <- c(low='#b52c0d', high='#1058b0')
cols <- c(low='#742b82ff', high='#a65a03ff')

cols_individual <- lighten(cols, amount=0.7)
names(cols_individual) <- names(cols)
```


### FFT

Analysis performed on a frontal cluster of channels to get better SNR.   

```{r, fig.width=2.3, fig.height=1.5}
p <- plot_feat_ind_lowhigh(df_eeg_ind, 
              col_name_eeg='z_meter_fft_subtr',
              col_name_coch='z_meter_fft_sound')

fname <- sprintf('%s_FFT', tools::file_path_sans_ext(fname_lowhigh))
save_fig(file.path(data_path, fname), p, width=2.3, height=1.4)
p
```
<br> 

Mixed model (factors: rhythm x tone)

```{r}
m <- lmer(z_meter_fft_subtr ~ rhythm * tone + (1|subject), data=df_eeg_ind)
a <- Anova(m)
knitr::kable(a)
```
<br> 

Posthoc tests low vs. high tone: 

```{r}
if (a[which(rownames(a) == 'rhythm:tone'), "Pr(>Chisq)"] < 0.05){
    
    df_posthoc <- df_eeg_ind %>% 
        group_by(rhythm) %>%
        group_modify(~posthoc_ttest_low_vs_high(.x, var_name_eeg='z_meter_fft_subtr'))
    
    df_posthoc$p <- p.adjust(df_posthoc$p, 'bonferroni')
    knitr::kable(df_posthoc)
    
} else if (a[which(rownames(a) == 'tone'), "Pr(>Chisq)"] < 0.05) {
    
    m_posthoc <- lmer(z_meter_fft_subtr ~ rhythm + tone + (1|subject), data=df_eeg_ind)
    emm <- emmeans(m_posthoc, 'tone')
    c <- contrast(emm, 'pairwise', adjust='bonferroni')
    knitr::kable(as.data.frame(c))
    
} else {
    
    print('no effect including tone signifianct...')

}
```
<br> 

T-test against 0 (fdr corrected): 
```{r}

df_posthoc <- df_eeg_ind %>% 
    group_by(rhythm, tone) %>% 
    group_modify(~ttest_0(.x, var_name='z_meter_fft_subtr'))

df_posthoc$p <- p.adjust(df_posthoc$p, method='fdr')

knitr::kable(df_posthoc)
```



<br><br><br> 

### ACF

Noise-subtracted acf was computed and averaged across **frontocentral** channels, separately for each participant.  

The zscore at meter-related lags was computed from the channel-averaged ACF, separately for each participant and condition.  

```{r, fig.width=2.3, fig.height=1.5}
p <- plot_feat_ind_lowhigh(df_eeg_ind, 
              col_name_eeg='z_meter_acf_subtr',
              col_name_coch='z_meter_acf_sound')

fname <- sprintf('%s_ACF', tools::file_path_sans_ext(fname_lowhigh))
save_fig(file.path(data_path, fname), p, width=2.3, height=1.4)
p

```
<br> 

Mixed model (factors: rhythm x tone)

```{r}
m <- lmer(z_meter_acf_subtr ~ rhythm * tone + (1|subject), data=df_eeg_ind)
a <- Anova(m)
knitr::kable(a)
```
<br> 

Posthoc tests low vs. high tone: 

```{r}
if (a[which(rownames(a) == 'rhythm:tone'), "Pr(>Chisq)"] < 0.05){
    
    df_posthoc <- df_eeg_ind %>% 
        group_by(rhythm) %>%
        group_modify(~posthoc_ttest_low_vs_high(.x, var_name_eeg='z_meter_acf_subtr'))
    
    df_posthoc$p <- p.adjust(df_posthoc$p, 'bonferroni')
    knitr::kable(df_posthoc)
    
} else if (a[which(rownames(a) == 'tone'), "Pr(>Chisq)"] < 0.05) {
    
    m_posthoc <- lmer(z_meter_acf_subtr ~ rhythm + tone + (1|subject), data=df_eeg_ind)
    emm <- emmeans(m_posthoc, 'tone')
    c <- contrast(emm, 'pairwise', adjust='bonferroni')
    knitr::kable(as.data.frame(c))

} else {
    
    print('no effect including tone signifianct...')
    
}

```

<br> 

T-test against 0 (fdr corrected): 
```{r}

df_posthoc <- df_eeg_ind %>% 
    group_by(rhythm, tone) %>% 
    group_modify(~ttest_0(.x, var_name='z_meter_acf_subtr'))

df_posthoc$p <- p.adjust(df_posthoc$p, method='fdr')

knitr::kable(df_posthoc)
```


### Correlation FFT~ACF

```{r}

res <- cor.test(df_eeg_ind$z_meter_fft_subtr, 
                df_eeg_ind$z_meter_acf_subtr, 
                method='pearson')

p <- plot_correlation_scatter(df_eeg_ind, 
                              'z_meter_fft_subtr',
                              'z_meter_acf_subtr',
                              corr_result=res, 
                              bins=15)


fname <- sprintf('%s_corrFftAcf', tools::file_path_sans_ext(fname_lowhigh))
save_fig(file.path(data_path, fname), p, width=4, height=4)
p

```

















